FictionEro - Affective Impact of Fiction

### 2025-12-03 analysis/analysis.qmd
Updated analysis
@DominiqueMakowski  good Rhat and ESS for individual and combined models with specified priors . Have added Relevance as slope for participants and started running them to see if they come back with reliable estimates

m <- readRDS("models/individual_models/ModelArousal_2_task_1.rds")
m <- readRDS("models/individual_models/ModelArousal_2_task_2.rds")
m <- readRDS("models/individual_models/ModelArousal_2_task_3.rds")
m <- readRDS("models/individual_models/ModelArousal_2_task_4.rds")
m <- readRDS("models/individual_models/ModelArousal_2_task_5.rds")
m <- readRDS("models/individual_models/ModelArousal_2_task_6.rds")

>>>>

# 
# m <- readRDS("models/individual_models/ModelArousal_2_task_1.rds")
# m <- readRDS("models/individual_models/ModelArousal_2_task_2.rds")
# m <- readRDS("models/individual_models/ModelArousal_2_task_3.rds")
# m <- readRDS("models/individual_models/ModelArousal_2_task_4.rds")
# m <- readRDS("models/individual_models/ModelArousal_2_task_5.rds")
# m <- readRDS("models/individual_models/ModelArousal_2_task_6.rds")
